Comparison of long and short amplicon metabarcoding for determination of fungal species diversity and spatial turnover

### 2019-08-13 writing/MSA2019_presentation.Rnw
Add rDNA and amplicon images to presentation

@@

\begin{frame}{Sequencing}
  \framesubtitle{Which region?}
  \small
  \begincols
  \begincol{0.5\linewidth}
    \begin{block}{ITS2 (gITS7-ITS4)}
        \begin{itemize}
          \tightlist
          \item Internally transcribed spacer between 5.8S and 26/28S (LSU) subunits of ribosomal RNA
          \item Usually 250--350 bp.
          \item ITS --- standard DNA barcode for fungi.
          \item Relatively good species-level resolution, and good database support.
          \item Cannot be aligned across larger taxonomic groups.
          \item Groups with variant (or absent) 5.8S not sequenced.
        \end{itemize}
      \end{block}
    \endcol
    \begincol{0.5\linewidth}
      \begin{block}{Full ITS + partial LSU (ITS1-LR5)}
        \begin{itemize}
          \tightlist
          \item Full ITS plus the 5' end of LSU; 1500-2000 bp.
          \item ITS -- resolution to separate closely related taxa.
          \item LSU -- can be aligned across fungi.
          \item Primers are more universal than gITS7.
          \item Long amplicon with alternating variable and conserved regions --- susceptible to chimera formation and breakage.
        \end{itemize}
      \end{block}
    \endcol
  \endcols
\end{frame}

>>>>

\begin{frame}{Metabarcoding}
\framesubtitle{rDNA regions}
\includegraphics[width=\linewidth]{rDNA}

\begin{tabular}{p{0.3\linewidht}p{0.3\linewidth}p{0.3\linewidth}}
SSU & ITS & LSU \\ \midrule
highly conserved w/variable regions & variable (5.8S conserved) & conserved w/variable regions \\
used for prokaryotes and all eukaryotes & official barcode for fungi & mostly used for fungi, early phylogenetics \\
\end{tabular}

\end{frame}

@@

\begin{frame}{Sequencing}
  \framesubtitle{Which region?}
  \small
  \includegraphics[width=\linewidth]{rDNA_amplicons}

  \begincols
  \begincol{0.5\linewidth}
    \begin{block}{ITS2 (gITS7-ITS4)}
        \begin{itemize}
          \tightlist
          \item Internally transcribed spacer between 5.8S and 26/28S (LSU) subunits of ribosomal RNA
          \item Usually 250--350 bp.
          \item ITS --- standard DNA barcode for fungi.
          \item Relatively good species-level resolution, and good database support.
          \item Cannot be aligned across larger taxonomic groups.
          \item Groups with variant (or absent) 5.8S not sequenced.
        \end{itemize}
      \end{block}
    \endcol
    \begincol{0.5\linewidth}
      \begin{block}{Full ITS + partial LSU (ITS1-LR5)}
        \begin{itemize}
          \tightlist
          \item Full ITS plus the 5' end of LSU; 1500-2000 bp.
          \item ITS -- resolution to separate closely related taxa.
          \item LSU -- can be aligned across fungi.
          \item Primers are more universal than gITS7.
          \item Long amplicon with alternating variable and conserved regions --- susceptible to chimera formation and breakage.
        \end{itemize}
      \end{block}
    \endcol
  \endcols
\end{frame}
